The \dealii{} Library, Version 8.4.0

### 2016-02-25 deal84.tex
mention MSVC

The major changes of this release are:
\begin{itemize}
\item Parallel triangulations can now be partitioned in ways that allow
  weighting cells differently
\item Improved support for mixed-type arithmetic throughout the library
\item A new triangulation type that supports parallel computations
  but ensures that the entire mesh is available on every processor
\item An implementation of the Rannacher-Turek element, as well as an
  element that extends the usual Q(p) elements by bubble functions
\item Second and third derivatives of finite element fields are now
  computed exactly.
\item The various \emph{Concepts}, or requirements on template parameters
  in the library, are now consistently labeled and documented as such.
\item The interface between finite elements, quadrature, mapping, and the
  FEValues class has been rewritten. It is now much better documented
\item  More than 140 other features and bugfixes.
\end{itemize}
Some of these will be detailed in the following section.
Information on how to cite \dealii{} is provided in Section \ref{sec:cite}.

@@

>>>>

The major changes of this release are:
\begin{itemize}
\item Parallel triangulations can now be partitioned in ways that allow
  weighting cells differently.
\item Improved support for mixed-type arithmetic throughout the library.
\item A new triangulation type that supports parallel computations
  but ensures that the entire mesh is available on every processor.
\item An implementation of the Rannacher-Turek element, as well as an
  element that extends the usual Q(p) elements by bubble functions.
\item Second and third derivatives of finite element fields are now
  computed exactly.
\item The various \emph{Concepts}, or requirements on template parameters
  in the library, are now consistently labeled and documented as such.
\item The interface between finite elements, quadrature, mapping, and the
  FEValues class has been rewritten. It is now much better documented.
\item Initial support for compiling with Visual C++ 2013 and 2015 under Windows
  has been added.
\item  More than 140 other features and bugfixes.
\end{itemize}
Some of these will be detailed in the following section.
Information on how to cite \dealii{} is provided in Section \ref{sec:cite}.

@@

\subsection{Visual C++ support}

The library can now be compiled under Windows with Visual C++ 2013 and
2015. The support is still experimental for the following reasons: First, we
currently only support static linking. This will slow down linking of
application code immensly.  Second, only a minimal testsuite is working, which
is mainly because static linking of thousands of test executables is not
viable. Therefore, we can not exclude the possibility of subtle bugs in the
library.  Finally, there is of course limited support for external packages.
